Hypertension and microbiome

### 2019-09-12 articletwo.Rmd
HT instead of MAP

dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq,
                               as.formula(sprintf("~ %s + %s", "MAP", paste0(var.CL, collapse = "+"))))

@@

results(dds) %>%
    as.data.frame %>%
    kable
```

>>>>

dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq,
                               as.formula(sprintf("~ %s + %s", "HT", paste0(var.CL, collapse = "+"))))

@@

saveRDS(dds, file = "rds/dds.rds")
#dds <- readRDS(file = "rds/dds.rds")

results(dds) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    kable
```
